Translation of B Implementations to the LLVM: Control and Modularity

### 2013-08-28 translation.tex
Added an example to validate translation rules for local variables. Updated translation prototype to handle local variables. Updated translation definition to reflect corrections.

\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|}
\hline
Example nº & 01 & 02 \\
\hline
variables & \yes & \yes \\
constants & \no & \yes \\
op. input & \yes & \no \\
op. output & \yes & \no \\
\hline
\multicolumn{3}{|c|}{instructions} \\
\hline
block & \yes & \no \\
local var & \no & \no \\
identity & \no & \no \\
becomes equal & \yes & \yes \\
operation call & \no & \no \\
condition & \yes & \no \\
case & \no & \no \\
assertion & \no & \no \\
sequence & \yes & \yes \\
while & \no & \no \\
\hline
\multicolumn{3}{|c|}{expressions} \\
\hline
succ & \no & \yes \\
pred & \no & \yes \\
+ & \yes & \no \\
- & \yes & \no \\
\hline
\multicolumn{3}{|c|}{formulas} \\
\hline
and & \no & \no \\
or & \no & \no \\
not & \no & \no \\
comparison & \yes & \yes \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\newcommand{\no}[0]{--}
\newcommand{\yes}[0]{$\circ$}
\begin{tabular}{|l|c|c|c|}
\hline
Example nº & 01 & 02 & 03 \\
\hline
variables & \yes & \yes & \yes \\
constants & \no & \yes & \no \\
op. input & \yes & \no & \yes \\
op. output & \yes & \no & \yes \\
\hline
\multicolumn{4}{|c|}{instructions} \\
\hline
block & \yes & \no & \yes \\
local var & \no & \no & \yes \\
identity & \no & \no & \yes \\
becomes equal & \yes & \yes & \yes \\
operation call & \no & \no & \no\\
condition & \yes & \no & \no\\
case & \no & \no & \no\\
assertion & \no & \no & \no\\
sequence & \yes & \yes & \yes\\
while & \no & \no & \no\\
\hline
\multicolumn{4}{|c|}{expressions} \\
\hline
int lit & \yes & \yes & \yes \\
bool lit & \yes & \yes & \no \\
vars & \yes & \yes & \yes \\
loc. vars & \no & \no & \yes \\
const & \no & \yes & \no \\ 
succ & \no & \yes & \no \\
pred & \no & \yes & \no \\
+ & \yes & \no & \no \\
- & \yes & \no & \no \\
\hline
\multicolumn{4}{|c|}{formulas} \\
\hline
and & \no & \no & \no \\
or & \no & \no & \no \\
not & \no & \no & \no \\
$<$ & \yes & \yes & \no \\
\hline
\end{tabular}
\end{center}
